---
title: "Introduction"
author: "Zixuan Li"
date: "5/2/2019"
output: html_document
---

```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
library(binomial)
```

## Binomial Functions

"binomial" is an R package that implements functions for calculating probabilities of a Binomial random variable, and related calculations such as the probability distribution, the expected value, variance, etc.

When X is a random variable that has a binomial distribution with n trials and probability
of success p, we write X ∼ Bin(n, p). As with most random variables.

## Binimial Variable

First create a binomial variable with specific a trial number and a probability number.
By calling the function bin_variable(), you can get a demonstration of your chosen values and a validity check on your chosen values.

```{r}
bin1 <- bin_variable(trials = 10, prob = 0.3)
bin1
```

If you want to get a full summary description of the object you have created, use the following method:
```{r}
bin1 <- bin_variable(trials = 10, p = 0.3)
binsum1 <- summary(bin1)
binsum1
```

## Mean

The expected number of successes in n trials or the expected value of a binomial distribution can be calculated by using:
```{r}
bin_mean(trials = 100, prob = 0.3)
```

## Variance

The variance of a binomial distribution can by calculated by using:
```{r}
bin_variance(trials = 100, prob = 0.3)
```

## Mode

For 0 < p < 1, the most likely number of success in n independent trials with probability p
of success on each trial is m, and it can be calculated by using:
```{r}
bin_mode(trials = 100, prob = 0.3)
```

## Skewness

Skewness is a measure of the asymmetry of the probability distribution of a random variable about its mean. The skewness of a binomial random variable can be calculated bt using:
```{r}
bin_skewness(trials = 100, prob = 0.3)
```

## Kurtosis

The Kurtosis is a measure of the “tailedness” of the probability distribution of a random variable.For a binomial random variable, its kurtosis can be calculated in this package by using:
```{r}
bin_kurtosis(trials = 100, prob = 0.3)
```

## Combinations

To calculate the number of combinations in which k successes can occur in n trials, use following method:
```{r}
bin_choose(n = 5, k = 2)
```

## Binomial Probability

To abtain a certain probability in which k successes can occur in n trials with probability p for each success to happen:
```{r}
bin_probability(success = 2, trials = 5, prob = 0.5)
```

## Binomial Distribution

Use bin_distribution() to generate the binomial distribution datafrmae of n trials, k successes, and probability p:
```{r}
bin_distribution(trials = 5, prob = 0.5)
```

To get a intuitive graph that displays the probability histogram of the binomial distribution object, include the following method to obtain the plot:
```{r}
dis1 <- bin_distribution(trials = 5, prob = 0.5)
plot(dis1)
```

## Binomial Cumulative Distribution

To return a data frame with both the probability distribution and the cumulative probabilities, you can include bin_cumulative() to make it happen:
```{r}
bin_cumulative(trials = 5, prob = 0.5)
```

To get the graoh of the cumulative distribution, use a similar method:
```{r}
dis2 <- bin_cumulative(trials = 5, prob = 0.5)
plot(dis2)
```

